Experiment 0 pilot

### 2016-09-24 experiments/e0/writeup/e0.Rmd
practicing for html upload

```{r getData}
if( file.exists('data.txt') ) 
	{
	d <- read.table("data.txt", header=FALSE) 
} else {
	system("cat ../experimentCode/output/*.dat > data.txt", wait=TRUE)
}
mynames <- list("gap", "target", "side", "vagueness", "pair", "Version", "Left",
								"Right", "Text", "Condition", "correctAnswer", "subject",
								"actualAnswer", "isCorrect", "rt")
names(d) <- mynames
d$obs <- 1:nrow(d)
d$trial <- 0
for (s in unique(d$subject)){
  d[d$subject==s, "trial"] <- 1:nrow(subset(d,subject==s))
}
# For some reason there is one rt of -6. Set it to NA
d[d$rt==-6,"rt"] <- NA
# make a df
d <- data.frame(
  obs = d$obs, 
  trial = d$trial, 
  subject = d$subject, 
  item = factor(d$pair, label = c("2:4", "3:5", "6:8", "7:9", "2:6", "7:3", "8:4", "5:9")),
  gap = factor(d$gap, levels = c("BigGap", "SmallGap"), labels = c("Big Gap", "Small Gap")), 
  quan = factor(d$target, levels = c("BigTarget", "SmallTarget"), labels = c("Big Target", "Small Target")), 
  vag = factor(d$vagueness, levels = c("Precise", "Vague"), labels = c("Crisp", "Vague")), 
  side = d$side, 
  err = 1 - d$isCorrect, 
  rt = d$rt)
d$subit <- "Not subitizable"
d$subit[d$item == "2:4"] <- "Subitizable"
d$subit[d$item == "3:5"] <- "Subitizable"
d$subit[d$item == "2:6"] <- "Subitizable"
d$subit[d$item == "7:3"] <- "Subitizable"
d$subit = as.factor(d$subit)
d <- subset(d, select = c("obs", "trial", "subject", "item", "gap", "quan", 
                          "vag", "subit", "side", "err", "rt"))
```

>>>>

```{r getData}
if( !file.exists('data.txt') ) {
	system("cat ../experimentCode/output/*.dat > data.txt", wait=TRUE) # concatenate the individual subject data files into one file 
} 
```

```{r}
# # This bit is for generating the PURE file
d <- read.table("data.txt", header=FALSE) # read in the data for all subjects
mynames <- list("gap_size", 
                "target_size", 
                "correct_side", 
                "vagueness",
                "pair", 
                "Version", 
                "Left",
                "Right", 
                "Text", 
                "Condition", 
                "correctAnswer",
                "subject",
                "actualAnswer",
                "isCorrect",
                "rt")
names(d) <- mynames
# For some reason there is one rt of -6. Set it to NA
d[d$rt==-6,"rt"] <- NA
d$observation <- 1:nrow(d)
d$trial <- 0
for (s in unique(d$subject)){
  d[d$subject==s, "trial"] <- 1:nrow(subset(d,subject==s))
}
d$item = ordered(d$pair, label = c("2:4", "3:5", "6:8", "7:9", "2:6", "7:3", "8:4", "5:9"))
d$subit <- "Not subitizable"
d$subit[d$item == "2:4"] <- "Subitizable"
d$subit[d$item == "3:5"] <- "Subitizable"
d$subit[d$item == "2:6"] <- "Subitizable"
d$subit[d$item == "7:3"] <- "Subitizable"
d$dotpair_id=d$item; d$item=NULL
d$subit = as.factor(d$subit)
d$gap_size = factor(d$gap_size, levels = c("BigGap", "SmallGap"), labels = c("Big", "Small"))
d$target_size = factor(d$target_size, levels = c("BigTarget", "SmallTarget"), labels = c("Big", "Small"))
d$vagueness = factor(d$vagueness, levels = c("Precise", "Vague"), labels = c("Crisp", "Vague")) 
d$is_error = 1 - d$isCorrect
d$dots_right=d$Right; d$Right=NULL
d$dots_left=d$Left; d$Left=NULL
dd <- subset(d, select=c(
  observation, subject, trial, gap_size, target_size, correct_side, dots_left, dots_right, dotpair_id, vagueness, Text, is_error, rt))
write.table(dd, file='pilot_experiment_data.txt', col.names=T, row.names=F, quote=F, sep='\t')
```

```{r}
# This bit is for carrying forward
d <- read.table("data.txt", header=FALSE) # read in the data for all subjects
mynames <- list("gap", "target", "side", "vagueness", "pair", "Version", "Left",
								"Right", "Text", "Condition", "correctAnswer", "subject",
								"actualAnswer", "isCorrect", "rt")
names(d) <- mynames
d$obs <- 1:nrow(d)
d$trial <- 0
for (s in unique(d$subject)){
  d[d$subject==s, "trial"] <- 1:nrow(subset(d,subject==s))
}
# For some reason there is one rt of -6. Set it to NA
d[d$rt==-6,"rt"] <- NA
# make a df
d <- data.frame(
  obs = d$obs, 
  trial = d$trial, 
  subject = d$subject, 
  item = factor(d$pair, label = c("2:4", "3:5", "6:8", "7:9", "2:6", "7:3", "8:4", "5:9")),
  gap = factor(d$gap, levels = c("BigGap", "SmallGap"), labels = c("Big Gap", "Small Gap")), 
  quan = factor(d$target, levels = c("BigTarget", "SmallTarget"), labels = c("Big Target", "Small Target")), 
  vag = factor(d$vagueness, levels = c("Precise", "Vague"), labels = c("Crisp", "Vague")), 
  side = d$side, 
  err = 1 - d$isCorrect, 
  rt = d$rt)
d$subit <- "Not subitizable"
d$subit[d$item == "2:4"] <- "Subitizable"
d$subit[d$item == "3:5"] <- "Subitizable"
d$subit[d$item == "2:6"] <- "Subitizable"
d$subit[d$item == "7:3"] <- "Subitizable"
d$subit = as.factor(d$subit)
d <- subset(d, select = c("obs", "trial", "subject", "item", "gap", "quan", 
                          "vag", "subit", "side", "err", "rt"))
```
